\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-11-22 paper.tex
update

% Robots are tasked to navigate, collecting sensory data of an unknown task space to map a slowly-varying field, denoted as $\vx$, (see Figure~\ref{fig:SecurityBreak}). The map comprises points of interest arranged on a grid, each associated with a slowly-changing value. Our goal is to find paths that minimize uncertainty and effectively reconstruct the field. We associate a Kalman Filter (KF)~(cf. \cite{anderson2012optimal}) to each point $j$, and use it to track the uncertainty through its estimated covariance $P_j$. The updates of the filters are based on measurements from the robot centered at $q$, and we use a Gaussian radial basis function  modeling spatially-varying measurement quality. The optimization objective $\varPhi(\vq)$ is written as the maximum uncertainty $\max_j P_{j}$ (detailed formulation can be found in \cite{yang2020multi}).
\end{example}
\begin{figure}
  \centering
  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{Grid world example of a task planned in a $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
\end{figure}

@@

We test the newly introduced security constraints to~\cref{example:map_exploration}, illustrated in~\cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}. The maximum velocity constraint $v_{max}=0.5m/dt$, time horizon $T=20$. %All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent. %robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}). %We apply the new security constraints on the map exploration problem shown in \Cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed. The 3-robot system is tasked to explore a $10m\times10m$ region with two forbidden regions \emph{Zone 2, 3}. The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.

We employ the APMAPF solver \cite{wardega2019resilience} to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}). %Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18. 
This result serves as the initial trajectory input for the ADMM solver. This obtained plan is then transformed to a continuous configuration space, addressing map exploration tasks. Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions. Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions. It's important to note that the secured attack-proof solution is initially infeasible in the continues setting, unless additional checkpoints (e.g., stationary security cameras) are incorporated (additional task added for agent 3 to visit the \emph{checkpoint} at time $8$). Further solutions to avoid these checkpoints are discussed in \Cref{sec:cross-trajectory}.

@@

\subsubsection{Limitations}\label{sec:reachability-discussion}
Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems. However, two primary challenges need to be addressed. Firstly, achieving a co-observation and reachability-secured plan may not always be feasible when robots are separated by obstacles or forbidden regions, making it impossible for them to establish co-observation schedules or find a reachability-secured path. For example, Agent 3 in Figure \ref{fig:ReachabilitySimulation} required an additional security checkpoint to create secured reachability areas. Secondly, meeting security requirements may impact overall system performance, as illustrated by the comparison between Figure \ref{fig:SecurityBreak} and \ref{fig:ReachabilitySimulation}. The introduction of security constraints led to the top left corner being unexplored by any robots. This trade-off between security and system performance is particularly significant given that system performance plays a crucial role in the decision to employ multi-agent systems. These challenges are addressed in Chapter \ref{sec:cross-trajectory} to ensure the effective use of planning with reachability and co-observation in securing multi-agent systems.

>>>>

% Robots are tasked to navigate, collecting sensory data of an unknown task space to map a slowly-varying field, denoted as $\vx$, (see Figure~\ref{fig:SecurityBreak}). The map comprises points of interest arranged on a grid, each associated with a slowly-changing value. Our goal is to find paths that minimize uncertainty and effectively reconstruct the field. We associate a Kalman Filter (KF)~(cf. \cite{anderson2012optimal}) to each point $j$, and use it to track the uncertainty through its estimated covariance $P_j$. The updates of the filters are based on measurements from the robot centered at $q$, and we use a Gaussian radial basis function  modeling spatially-varying measurement quality. The optimization objective $\varPhi(\vq)$ is written as the maximum uncertainty $\max_j P_{j}$ (detailed formulation can be found in \cite{yang2020multi}).
\end{example}
\begin{figure}
  \centering
  \subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
  \caption{\new{(a) Grid world example of a task planned in a $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
\end{figure}

@@

We test the newly introduced security constraints with~\cref{example:map_exploration}, illustrated in~\cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}. The maximum velocity constraint $v_{max}=0.5m/dt$, time horizon $T=20$. %All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent. %robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}). %We apply the new security constraints on the map exploration problem shown in \Cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed. The 3-robot system is tasked to explore a $10m\times10m$ region with two forbidden regions \emph{Zone 2, 3}. The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.

We employ the APMAPF solver \cite{wardega2019resilience} on a 8 by 8 grid world with similar setup to generate a MAPF plan with a co-observation schedule in a grid-world application (Fig.\ref{fig:Grid-example-application}). This result is transformed to a continuous configuration space and serves as the initial trajectory input for the ADMM solver with additional task function targeting the map exploration task. Co-observation schedules are set up using the APMAPF algorithm for two forbidden regions. Reachability constraints are added to ensure an empty intersection between all robots' reachability regions during co-observations and the forbidden regions. {\news It is important to emphasize that an APMAPF solution does not guarantee existence, nor does it ensure a successful transition to the continuous configuration space. In this cases, while an APMAPF solution may be found, the secured, attack-proof solution becomes infeasible in the continuous setting because the robots' mobility is no longer restricted to adjacent grids. Additional security measures, such as stationary security cameras or surveillance robots, need to be incorporated. For instance, in this scenario, we deploy a security camera as additional checkpoint to observe agent 3 at time $8$ to ensure security.}

@@

\subsubsection{Limitations}\label{sec:reachability-discussion}
Our solution demonstrates the potential of planning with reachability and co-observation to enhance the security of multi-agent systems.{\news However, two primary challenges need to be addressed. Firstly, achieving a co-observation and reachability-secured plan is not always feasible, particularly when obstacles or restricted regions separate the robots, preventing them from establishing co-observation schedules or finding reachability-secured paths. For example, agent 3 in~\cref{fig:ReachabilitySimulation} requires additional security measures to create secured reachability areas. Secondly, security requirements can impact overall system performance, as illustrated by the comparison between~\cref{fig:SecurityBreak} and \cref{fig:ReachabilitySimulation}. The introduction of security constraints resulted in the top left corner remaining unexplored by any robots. This trade-off between security and system performance is particularly significant as system performance is a key factor in the decision of multi-agent system deployments. These challenges are further addressed in \cref{sec:cross-trajectory}, ensuring the effective integration of reachability and co-observation in securing multi-agent systems.}
